
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\PassOptionsToPackage{pdfpagelabels=false}{hyperref}
\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{green} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\newcommand\Colorhref[3][blue]{\href{#2}{\small\color{#1}#3}}

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=.85]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Antoine} % Your first name
\familyname{Desbordes} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Optimization engineer}
\email{antoine.desbordes@gmail.com}
\social[linkedin]{antoine-desbordes-59142310/}
\social[github]{antoine-de} 

\extrainfo{May 31\textsuperscript{st} 1985}
% \photo[70pt][0.4pt]{pictures/photo} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}
%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title
%----------------------------------------------------------------------------------------
%	Skills SECTION
%----------------------------------------------------------------------------------------

\section{Skills \& Abilities}

\cvitem{Programming Languages}{Rust, Advanced C++, Python}
\cvitem{Optimization}{Graph theory (mostly shortest path), mathematical programming, constraint programming, local search, decision tree, rules engine}
\cvitem{Tools}{Linux, Docker, ElasticSearch, Postgres, GIS, Boost}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Work Experience}

\cventry{Oct 2017 -- Present}{Software Engineer}{\textsc{Qwant Research}}{Paris}{}{
  Creation of Qwant Maps, an \Colorhref{https://github.com/QwantResearch/qwantmaps}{open source} map service for \Colorhref{https://qwant.fr}{Qwant}, a French search engine focused on respecting privacy.
    \newline{}
    Design of a scalable vector tile architecture and development of a worldwide geographic search engine.
    \newline{}
    Core developer on:
    \begin{itemize}
      \item \Colorhref{https://github.com/CanalTP/mimirsbrunn/}{mimirsbrunn}: worldwide geographic search engine (geocoder)
      \item \Colorhref{https://github.com/osm-without-borders/cosmogony/}{cosmogony}: tool to process geographic regions 
    \end{itemize}
}

\cventry{Nov 2013 -- Sep 2017}{Software Engineer}{\textsc{Kisio Digital}}{Paris}{}{
    Software engineer in the operations research team in charge of \Colorhref{http://navitia.io}{Navitia}.
    \newline{}
    Navitia is a \Colorhref{https://github.com/CanalTP/navitia}{opensource} traveler information software providing features like multi-modal journeys,
     timetables, and isochrones.
    \newline{}
    It is an API build with micro-service components written in C++, python and rust and can handle real-time data.
    \newline{}
    Navitia's core feature, the journey planning, uses various algorithms as Djisktra's and a custom version of 
    \Colorhref{https://www.microsoft.com/en-us/research/wp-content/uploads/2012/01/raptor_alenex.pdf}{RAPTOR}, a multi objective dynamic programming algorithm mixed with branch and bound.
}

\cventry{Oct 2007 -- Nov 2013}{Optimization Engineer}{\textsc{Eurodecision}}{Paris}{}{
    \textsc{Eurodecision} is a consulting firm specialized in Optimization.\newline{}
    Example of missions carried out:
    \begin{itemize}
    \item \textbf{Air France} Long term mission on:
        \begin{itemize}
            \item crew scheduling;
            \item architecture of the new yield management system and development of the cancellation forecasting module;
            \item model of the impacts of a flight program change on the income and optimization of the flight program.
        \end{itemize}
    \item \textbf{CSDL} (European research project): Stochastic optimization for uncertainty handling in product design;
    \item \textbf{ERDF}: Shortest path and vehicle routing implementation for the deployment of the Linky electric meter;
    \item \textbf{Tegaz}: Leading the development of an optimization engine to balance a gas network;
    \item \textbf{AAA Data}: Rule based engine to aggregate heterogeneous data sources.
    \end{itemize}
}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{French}{Native speaker}{}
\cvitemwithcomment{English}{Fluent}{Daily used at work. 7.5/9 "good user" at the IELTS exam.}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2003 -- 2007}{École des Mines de Nantes}{}{}{\textit{Computer science and operations research}}{}

\cventry{2002 -- 2003}{Classe Préparatoire aux Grandes Ecoles}{Lycée Claude Bernard, Paris}{}{}{}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

% \section{Interests}

% \renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
% \cvlistdoubleitem{Piano}{}
% \cvlistitem{Baseball}

\end{document}




